% BEGIN
\documentclass{article}

% UNICODE
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{wasysym}
\usepackage{oplotsymbl}

% LAYOUT
\usepackage{calc}
\newlength{\unit}\setlength{\unit}{9.5625pt} % ONE- SIXTY-FOURTH PAGE WIDTH
\newlength{\marginheaderl}\setlength{\marginheaderl}{0\unit}
\newlength{\widthheader}\setlength{\widthheader}{24\unit}
\newlength{\marginl}\setlength{\marginl}{4\unit}
\newlength{\marginr}\setlength{\marginr}{4\unit}
\usepackage[
    paperwidth=612pt, 
    paperheight=792pt, 
    margin=\marginr, 
    top=8\unit, 
    left=\marginheaderl + \widthheader + \marginl, 
    bottom=8\unit, 
    marginparsep=\marginl, 
    marginparwidth=\widthheader
]{geometry}

% PACKAGES
\usepackage[overlay]{textpos}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{fp}

% SUPPRESS UNDERFULL BOX WARNINGS
% \hbadness=999999

% HYPERLINKS HAVE ODD FORMATTING
\hypersetup{%
  colorlinks=false,% HYPERLINKS WERE RED
  linkbordercolor=red,% THEY HAD A RED BORDER
  pdfborderstyle={/S/U/W 0}% THEY HAD A BORDER AND 1PT UNDERLINE
}

% FONTS
\usepackage{TheanoDidot} % ROMAN
\usepackage{Chivo} % SANS_SERIF
\usepackage{inconsolata} % MONOSPACE
\renewcommand{\familydefault}{\sfdefault}
\newcommand{\defaultfontsize}{\fontsize{\unit}{1\unit}\selectfont}

% FORMATTING
\linespread{1}
\setlength\parindent{0pt}
\reversemarginpar
\pagenumbering{gobble}

% SECTIONS
\newcommand{\sectionskip}{\vspace{4\unit}}
\newcommand{\makeHeader}[1]{
    \leavevmode\marginpar{%
        \ttfamily
        \defaultfontsize
        \textblockcolor{black}%
        \begin{flushright}\leavevmode\leaders\hbox{\space»}\hfill\kern0pt\uppercase{\space#1}\end{flushright}
    }%
}

% DOCUMENT
\begin{document}
    \defaultfontsize
    \raggedright

    \makeHeader{%
        Motion Graphics\\ 
        \vspace{\baselineskip}
        CPTR.346\\
        Fall 2020 | Southwestern College\\
        Professor Evan Daniel\\
        Evan.Daniel@SCKans.edu\\
        \vspace{\baselineskip}
        Christy 12\\ 
        TU+TH \space2:35PM- 3:50PM\\
        Office Hours M-F 12:00PM- 1:00PM\\
    }%
    Motion Graphics is a powerful domain that asks of us facility in using and combining the tools of vector graphics, digital video editing, and the custom tools of animation.  It is in the orchestration of these tools that we find a powerful medium capable of expressing stories with a nuance and freedom that makes motion graphics a significant contemporary art form.  

    \vspace{\baselineskip}We will use industry-standard software (Toon Boom Harmony) and analyze professional examples to develop increased sophistication in the problems inherent in motion graphics and animation.  Simultaneously, we will discuss relevant texts and hold regular critiques to further the development of our individual practices.  

    \sectionskip\makeHeader{Course Catalog Listing}%
    CPTR346/Lecture/A - Motion Graphics | Credits 3.00
    A course in the creation of digital productions combining multiple elements for gaming, commercial video or web presentations. Video shooting and editing techniques taught in the course are combined with audio, sound and image manipulation, 2D and 3D graphics, interactive authoring and web creation techniques learned in prerequisite courses. Prerequisite: COMM 205, CPTR 211, COMM 216, CPTR 220, CPTR 240 or consent of instructor. Credit 3 hours.

    \sectionskip\makeHeader{Course Deliverables}%
    \vspace{-1.75\baselineskip}
    \begin{itemize}[leftmargin=*]
        \item Understanding of the motion graphics workflow, including common problems and techniques used across software.
            \begin{itemize}
                \item\textit{50 minutes in-class per week}.
                \item\textit{2 hours 20 minutes out-of-class per week}.
            \end{itemize}
        \item Technical fluency in motion graphics software and media.  
            \begin{itemize}
                \item\textit{50 minutes in-class per week}.
                \item\textit{3 hours 30 minutes out-of-class per week}.
            \end{itemize}
        \item Ability to offer considered and insightful analysis of motion graphics; knowledge of historical and contemporary motion graphics examples; familiarity with theoretical texts related to motion graphics.  
            \begin{itemize}
                \item\textit{50 minutes in-class per week}.
                \item\textit{1 hour 10 minutes out-of-class per week}.
            \end{itemize}
    \end{itemize}
    \vspace{-\baselineskip}

    \sectionskip\makeHeader{Attendance}%
    Attendance can be in-person or through Zoom.  Attendance will be recorded, but there is no penalty for absences (including "total absence"; neither in-person nor on Zoom).  

    \vspace{\baselineskip}If a student is absent on a day an assignment is due, they are required to set up a meeting with the instructor to be held within one academic week (or five "business" days) of returning to class.  It is their responsibility to set up this meeting, to be prepared to present their work, and to allot ten minutes to discuss each assignment.  If they do not do so, they will receive a grade of 0 for the assignment.  
    
    \sectionskip\makeHeader{Assessment}%
    Assignments will be assessed through class discourse (the dialogue between instructor, student, and peers).  Assessment criteria will be both the formal outcome as well as the student's demonstrated understanding of the assignment in discussion.

    \vspace{\baselineskip}Each assignment will have a grade recorded between 0 to 1 (e.g. "0.5"; "0.875").  At the end of the semester, these grades will be averaged with a perfect grade of 1 and multiplied by 100 (e.g., if the student's average grade is 0.75, their final grade will be (0.75 + 1.00) / 2 * 100, or 87.5\%).  

    \sectionskip\makeHeader{Ethics}%
    This course is a space where we acknowledge and value the agency of each of our peers and the diversity of our community.  To be consistent with those values, all communication within the course --- whether in the form of spoken word, submitted assignments, online communication, or any other form --- must allow all other individuals in the course to freely participate.
    
    \vspace{\baselineskip}Students whose verbal communication prevents or precludes others from being part of our community or discourse will be asked to leave the course meeting, and can be made subject to further academic discipline. Submitted work that prevents or precludes others from being part of our community or discourse will not be assessed, with no points awarded.  Note that plagiarism is detrimental to our discourse and therefore falls under this category.

    \sectionskip\makeHeader{Southwestern College\\ Builder Community Health Pledge}%
    Our pledge to shared responsibility and community health: 
    \begin{itemize}
        \item I will know and check for COVID-19 symptoms daily
        \item I will stay in my residence when I have a temperature about 100 degrees Fahrenheit
        \item I will practice frequent hand-washing
        \item I will maintain 6-feet of social distance wherever possible
        \item I will wear a mask in buildings when outside of my residence room or individual office
        \item I will avoid large social gatherings
        \item I will limit my personal travel as possible and necessary
        \item I will follow and abide by directions and guidelines of college and Public Health officials related to the need to identify and contact trace any possible COVID-19 cases or exposures
    \end{itemize}
    I understand that the health of everyone in our Builder community is dependent upon shared responsibility, and I will do my part to help protect my community.  I will demonstrate care and respect for others.  This is the Builder Way.  
    
    \sectionskip\makeHeader{Southwestern College\\ Disability Services Statement}%
    Students in this course who have a disability that might prevent them from fully demonstrating their academic abilities should contact Steve Kramer, Disability Services Coordinator as soon as possible to initiate disability verification and discuss accommodations.  Steve Kramer’s office is located in the basement of the Christy Administration building, through the double glass doors.  He can be reached at (620) 229-6307 or at disability.services@sckans.edu. In the event of his absence, Arthur Smith, Disability Services Coordinator for Professional Studies will respond. Please also consult the \href{https://www.sckans.edu/student-services/student-success-and-retention/disability-services/}{\color{blue}\bfseries Disability Services Webpage}.
    
    \vspace{\baselineskip}Southwestern College has an office specifically designed to help you, the student, with any issues you may have.  We will guide you to the help you need and have the expertise to make difficult problems more manageable.  You can reach us at Student.Success@sckans.edu, you will see us around campus or you can come by the office in the basement of Christy through the double glass doors.  We are here for your success.

    \sectionskip\makeHeader{Required Resources}%
    \href{https://www.toonboom.com/products/harmony}{\color{blue}\bfseries Toon Boom Harmony Essentials}\\
    Toon Boom Harmony is industry-standard software for creating animations; it is used by well-known productions such as The Simpsons, Family Guy, Rick and Morty, Adventure Time, South Park, Star Wars: The Clone Wars, and many more.  It is based in the principles of vector graphics (data is stored as bezier curves, a simple means of recording curvature).  This data is combined with time-based-editing and animation tools to form a powerful software.
 
\end{document}